Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-05-22 Scripts/Initial_Analysis.Rmd
Should be ready to run in Beasty Beast

GetCentroids <- function(taxon_key,
                         year, 
                         data_type = "Catch",
                         ensemble, 
                         # path,
                         Neighbours,
                         eez_centroid){

@@

  Spp_Dist <- read_dbem_ens(
    taxon_key = taxon_key,
    year = year,
    data_type = data_type,
    ensemble = ensemble,
    path = my_path("D",extra_path = "/DBEM")
  )

@@

# Test_centroids <- GetCentroids(taxon_key = 600004,
#              year = year_df$year,
#              # data_type = data,
#              ensemble = 102,
#              # path = path,
#              Neighbours = Neighbours,
#              eez_centroid = eez_centroid
#              )
# head(Test_centroids)
# unique(Test_centroids$ensemble)
# unique(Test_centroids$neigh)
# 
# ggplot(Test_centroids) +
#   geom_line(
#     aes(
#       x = year,
#       y = distance,
#       color = eez_name
#     )
#   )

@@

TransIndex <- function(Centroids, # Expecting the results from the GetCentroids function
                       Ids, # A numeric value representing a neighbouring interaction
                       Hist_y = 2000){ # The LAST year of Historical data

  # Filter data by neighbouring ID
  Centroids_id <- Centroids %>% 
    filter(neighbour_id %in% Ids)

  EEZ_ids <- Neighbours %>% 
    filter(neighbour_id %in% Ids)

@@

  # Plot the result, bruh
  # For testing
  ggplot() +
    geom_line(data = mean_sd_index,
              aes(
                x = year,
                y = trend
              )
    ) +
    geom_ribbon(data = mean_sd_index,
                aes(x=year,
                    ymin=historic_sd$hist_mean-historic_sd$noise,
                    ymax=historic_sd$hist_mean+historic_sd$noise),
                alpha = 0.5,
                fill = "grey50"
    ) +
    geom_line(data = mean_sd_index,
              aes(
                x = year,
                y = historic_sd$hist_mean
              ),
              colour = "grey50"
    ) +
    geom_point(data = subset(mean_sd_index, trend > (historic_sd$hist_mean+historic_sd$noise) | trend < (historic_sd$hist_mean-historic_sd$noise)),
               aes(
                 x = year,
                 y = trend,
                 colour = "red",
               ),
               shape = 1,
               size = 3
    ) +
    geom_vline(xintercept = 2000,colour="blue",alpha = 0.5) +
    scale_x_continuous(breaks = seq(1950,2100,5)) +
    theme_classic() +
    ggsave("plot_example.jpg",
       plot = last_plot(),
       width = 10,
       height = 8,
       units = "in",
       path = my_path("R")
       )

@@

    # First step
    # Call Get centroids fucntion for centroids data per ensemble
    Step_one <- bind_rows(
      lapply(ensemble_list,
             GetCentroids,
             taxon_key = taxon_key,
             year = year,
             data_type = data_type,
             Neighbours = Neighbours,
             eez_centroid = eez_centroid)
    )

@@

  # GetTransIndex(
  #   taxon_key = 600004,
  #   ensemble_list = ensemble_list[1:2],
  #   year = year,
  #   Hist_y = 2000,
  #   data_type = "Abd",
  #   Neighbours = Neighbours,
  #   eez_centroid = eez_centroid
  # )

@@

>>>>

GetCentroids <- function(taxon_key,
                         year, 
                         data_type = "Catch",
                         ensemble, 
                         path,
                         Neighbours,
                         eez_centroid
                         ){

@@

  Spp_Dist <- read_dbem_ens(
    taxon_key = taxon_key,
    year = year,
    data_type = data_type,
    ensemble = ensemble
  )

@@

# GetCentroids(taxon_key = 600006,
#              year = year_df$year[1:5],
#              data_type = "Catch",
#              ensemble = 102,
#              Neighbours = Neighbours,
#              eez_centroid = eez_centroid
#              )

# head(Test_centroids)
# unique(Test_centroids$ensemble)
# unique(Test_centroids$neigh)
# 
# ggplot(Test_centroids) +
#   geom_line(
#     aes(
#       x = year,
#       y = distance,
#       color = eez_name
#     )
#   )

@@

TransIndex <- function(Centroids, # Expecting the results from the GetCentroids function
                       Id, # A numeric value representing a neighbouring interaction (ONE!)
                       Hist_y = 2000,
                       Plot = F){ # The LAST year of Historical data

  # Filter data by neighbouring ID
  Centroids_id <- Centroids %>% 
    filter(neighbour_id %in% Id)

  EEZ_ids <- Neighbours %>% 
    filter(neighbour_id %in% Id)

@@

  # For testing
  if(Plot == T){
  # Plot the result, bruh

  # Step to determine if data exists
  Plot_Test <- nrow(subset(mean_sd_index, trend > (historic_sd$hist_mean+historic_sd$noise) | trend < (historic_sd$hist_mean-historic_sd$noise)))>0

  ggplot() +
    geom_line(data = mean_sd_index,
              aes(
                x = year,
                y = trend
              )
    ) +
    geom_ribbon(data = mean_sd_index,
                aes(x=year,
                    ymin=historic_sd$hist_mean-historic_sd$noise,
                    ymax=historic_sd$hist_mean+historic_sd$noise),
                alpha = 0.5,
                fill = "grey50"
    ) +
    geom_line(data = mean_sd_index,
              aes(
                x = year,
                y = historic_sd$hist_mean
              ),
              colour = "grey50"
    ) +
    # Conditional, will only plot circles if the data exists
    {if(Plot_Test)geom_point(data = subset(mean_sd_index, trend > (historic_sd$hist_mean+historic_sd$noise) | trend < (historic_sd$hist_mean-historic_sd$noise)),
               aes(
                 x = year,
                 y = trend,
                 colour = "red",
               ),
               shape = 1,
               size = 3
    )
      } +
    geom_vline(xintercept = 2000,colour="blue",alpha = 0.5) +
    scale_x_continuous(breaks = seq(1950,2100,5)) +
    theme_classic() +
    ggsave(paste(taxon_key,Id,"plot_example.jpg",sep="_"),
       plot = last_plot(),
       width = 10,
       height = 8,
       units = "in",
       path = my_path("R")
       )

@@

    # First step
    # Call Get centroids fucntion for centroids data per ensemble
    Step_one <- bind_rows(
      lapply(ensemble_list[1:2],
             GetCentroids,
             taxon_key = taxon_key,
             year = year_df$year,
             data_type = data_type,
             Neighbours = Neighbours,
             eez_centroid = eez_centroid
             )
    )

@@

  # GetTransIndex(
  #   taxon_key = 600006,
  #   ensemble_list = ensemble_list,
  #   year = year_df$year,
  #   Hist_y = 2000,
  #   data_type = "Abd",
  #   Neighbours = Neighbours,
  #   eez_centroid = eez_centroid
  # )

@@

## ----------------- ##
# Data needed for estimating year of emergence
# Note: Use repo = F when running on the Beast or Hall1000
## ----------------- ##
